Downward shortwave solar irradiance enhancement by clouds.

### 2024-05-23 article/article.Rmd
Commit 2024-05-23 16:10

We computed the daily trend of the mean OIR of CE <!--
(Figure\nobreakspace{}\ref{fig:CEmeanDaily}), --> using a first-order autoregressive
model with a lag of one day, with the 'maximum likelihood' fitting method
[@Gardner1980; @Jones1980] by implementing the function 'arima' from the library
'stats' of the R programming language [@RCT2023]. The trends are reported together
with the $2\sigma$ error.  We observed a negligible change of
$`r round(dailyCE[var == "GLB_diff.mean", Tmod_Estimate], 3)`\pm
`r round(2 * dailyCE[var == "GLB_diff.mean", Tmod_Std..Error], 3)`\,W/m^2/y$
on the mean OIR.
<!-- ```{r CEmeanDaily, echo=FALSE, fig.cap="Daily mean values and trend of the CE over irradiance."} -->
<!-- knitr::include_graphics("../images/P_daily_trend-1.png") -->
<!-- ``` -->
Although, the previous result is closer to the raw data, we preferred to present the
annual statistics, that give a more clear picture about the long term CE trends.
Hence, we calculated the annual values from the one-minute measurements.  Despite the
very weak statistical significance of the mean OIR trend, the annual number of CE
occurrences shows a steady increase of
$`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm
`r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,\text{cases}/y$
(Figure\nobreakspace{}\ref{fig:P-energy-N}).
Subsequently, the mean annual energy of the CE events is increasing with a rate of
$`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,kJ/y$
(Figure\ \ref{fig:P-energy-sum}), witch follows the trend of the number of
occurrences.  We have to note that the energy related to the CE events can not be
directly linked with the total energy balance of the atmosphere. The net solar
radiation of the region is not increased, but rather redistributed through the CE
events.  This also is depicted by the "instantaneous" values of irradiance (average
over one minute), that can exceed the equivalent clear sky irradiance to a
considerable level.

@@

Another interesting aspect of the CE cases, is their seasonal cycle. In
Figure\nobreakspace{}\ref{fig:relative-month-occurancies}, we have the box plot
(whisker plot), where the values have been normalized by the highest median value,
that occurs on June.  Although the number of occurrences has a wide spread throughout
the study period, the most active period of CE occurrences is during May and June.
During the Winter (December -- February) the CE cases are about $25\,\%$ of the maximum.
For the rest months the occurrences gradually ramp between the maximum and minimum.

@@

The distribution of the CE over irradiance spreads uniformly
Figure\nobreakspace{}\ref{fig:ovir-distribution}. Where there is an inverse relation
between the events frequency and events intensity. This is expected as, the stronger
the CE events become, the rarer the particular atmospheric and sun conditions
occur.

```{r ovir-distribution, echo=FALSE, fig.cap="Distribution of CE over irradiance"}
knitr::include_graphics("../images/P-relative-distribution-diff-1.png")
```

@@

In order to further study the characteristics of the CE events, we grouped the single
minute CE events, to continuous CE groups (CEG). Thus, a CEG consists of one or more
successive CE cases, and can have a duration of multiple of minutes.  We have
identified `r ST_G0[, .N]` groups, where the group with the longest duration lasted
`r ST_G0[, max(GLB_diff.N)]` minutes on
`r strftime(ST_G0[which.max(GLB_diff.N), Date], "%d\\ %B %Y")`.
By examining the frequency distribution of the CEG durations
(Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}), we can conclude that
longer durations are getting increasingly rare, with durations above 10 minutes very
rare.

```{r ceg-duration-distribution, echo=FALSE, fig.cap="Distribution of CE groups"}
knitr::include_graphics("../images/groups-1.png")
```

>>>>

We computed the daily trend of the mean OIR of CE <!--
(Figure\nobreakspace{}\ref{fig:CEmeanDaily}), --> using a first-order autoregressive
model with a lag of one day, with the 'maximum likelihood' fitting method
[@Gardner1980; @Jones1980] by implementing the function 'arima' from the library
'stats' of the R programming language [@RCT2023]. The trends are reported together
with the $2\sigma$ error.  We observed a negligible change of
$`r round(dailyCE[var == "GLB_diff.mean", Tmod_Estimate], 3)`\pm
`r round(2 * dailyCE[var == "GLB_diff.mean", Tmod_Std..Error], 3)`\,W/m^2/y$
on the mean OIR.
<!-- ```{r CEmeanDaily, echo=FALSE, fig.cap="Daily mean values and trend of the CE over irradiance."} -->
<!-- knitr::include_graphics("../images/P_daily_trend-1.png") -->
<!-- ``` -->
Although, the previous result is closer to the raw data, we preferred to present the
annual statistics, that give a more clear picture about the long term CE trends.
Hence, we calculated the annual values from the one-minute measurements.  Despite the
very weak statistical significance of the mean OIR trend, the annual number of CE
occurrences shows a steady increase of
$`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm
`r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,\text{cases}/y$
(Figure\nobreakspace{}\ref{fig:P-energy-N}).
Subsequently, the mean annual energy of the CE events is increasing with a rate of
$`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,kJ/y$
(Figure\ \ref{fig:P-energy-sum}), witch follows the trend of the number of CE
occurrences.  We have to note that the energy related to the CE events can not be
directly linked with the total energy balance of the atmosphere. The net solar
radiation of the region is not increased, but rather redistributed through the CE
events.  This also is depicted by the "instantaneous" values of irradiance (average
over one minute), that can exceed the equivalent clear sky irradiance to a
considerable level.

@@

Another interesting aspect of the CE cases occurrences, is their seasonal cycle. In
Figure\nobreakspace{}\ref{fig:relative-month-occurancies}, we have a monthly box plot
(whisker plot), where the values have been normalized by the highest median value,
that occurs on June.  Although the number of occurrences has a wide spread throughout
the study period, the most active period of CE occurrences is during May and June.
During the Winter (December -- February) the CE cases are about $25\,\%$ of the maximum.
For the rest months the occurrences gradually ramp between the maximum and minimum.
These seasonality is a combinations of the clouds occurrences, and the relevant
position of the sun during the year. Unfortunately, the lack of detailed data of cloud
formation, type and location is not allowing further analysis.

@@

The distribution of the CE over irradiance intensity follows an exponential decline
Figure\nobreakspace{}\ref{fig:ovir-distribution}, where there is an inverse relation
between the events frequency and events intensity. This is expected as, the stronger
the CE events become, the rarer the particular atmospheric and sun conditions will
occur. This is indicative to the magnitude and probability of the expected OIRs
events over Thessaloniki.

```{r ovir-distribution, echo=FALSE, fig.cap="Distribution of CE over irradiance magnitude."}
knitr::include_graphics("../images/P-relative-distribution-diff-1.png")
```

@@

In order to further study the characteristics of the CE events, we grouped the single
minute CE events to continuous CE groups (CEG). Thus, a CEG consists of one or more
successive CE cases, and can represent cloud enhancement conditions spanning a
duration of multiple minutes.  We have identified `r ST_G0[, .N]` groups, where
the group with the longest duration lasted
`r ST_G0[, max(GLB_diff.N)]` minutes on
`r strftime(ST_G0[which.max(GLB_diff.N), Date], "%d\\ %B %Y")`.
By examining the frequency distribution of the CEG durations
(Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}), we can conclude, that
although we detected some CEG with durations longer than an hour, about $80\,\%$ of the CEG have a duration of less than 5 minutes.

```{r ceg-duration-distribution, echo=FALSE, fig.cap="Distribution of CE groups duration in minutes."}
knitr::include_graphics("../images/groups-1.png")
```

### 2024-05-23 article/article.tex
Commit 2024-05-23 16:10

We computed the daily trend of the mean OIR of CE using a first-order
autoregressive model with a lag of one day, with the `maximum
likelihood' fitting method \citep{Gardner1980, Jones1980} by
implementing the function `arima' from the library `stats' of the R
programming language \citep{RCT2023}. The trends are reported together
with the \(2\sigma\) error. We observed a negligible change of
\(0.087\pm 0.08\,W/m^2/y\) on the mean OIR. Although, the previous
result is closer to the raw data, we preferred to present the annual
statistics, that give a more clear picture about the long term CE
trends. Hence, we calculated the annual values from the one-minute
measurements. Despite the very weak statistical significance of the mean
OIR trend, the annual number of CE occurrences shows a steady increase
of \(45.6\pm 21.9\,\text{cases}/y\)
(Figure\nobreakspace{}\ref{fig:P-energy-N}). Subsequently, the mean
annual energy of the CE events is increasing with a rate of
\(116.9\pm 67.8\,kJ/y\) (Figure~\ref{fig:P-energy-sum}), witch follows
the trend of the number of occurrences. We have to note that the energy
related to the CE events can not be directly linked with the total
energy balance of the atmosphere. The net solar radiation of the region
is not increased, but rather redistributed through the CE events. This
also is depicted by the ``instantaneous'' values of irradiance (average
over one minute), that can exceed the equivalent clear sky irradiance to
a considerable level.

@@

Another interesting aspect of the CE cases, is their seasonal cycle. In
Figure\nobreakspace{}\ref{fig:relative-month-occurancies}, we have the
box plot (whisker plot), where the values have been normalized by the
highest median value, that occurs on June. Although the number of
occurrences has a wide spread throughout the study period, the most
active period of CE occurrences is during May and June. During the
Winter (December -- February) the CE cases are about \(25\,\%\) of the
maximum. For the rest months the occurrences gradually ramp between the
maximum and minimum.

@@

The distribution of the CE over irradiance spreads uniformly
Figure\nobreakspace{}\ref{fig:ovir-distribution}. Where there is an
inverse relation between the events frequency and events intensity. This
is expected as, the stronger the CE events become, the rarer the
particular atmospheric and sun conditions occur.

@@

\caption{Distribution of CE over irradiance}\label{fig:ovir-distribution}
\end{figure}

@@

In order to further study the characteristics of the CE events, we
grouped the single minute CE events, to continuous CE groups (CEG).
Thus, a CEG consists of one or more successive CE cases, and can have a
duration of multiple of minutes. We have identified 28468 groups, where
the group with the longest duration lasted 140 minutes on 07~July 2013.
By examining the frequency distribution of the CEG durations
(Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}), we can
conclude that longer durations are getting increasingly rare, with
durations above 10 minutes very rare.

@@

\caption{Distribution of CE groups}\label{fig:ceg-duration-distribution}
\end{figure}

>>>>

We computed the daily trend of the mean OIR of CE using a first-order
autoregressive model with a lag of one day, with the `maximum
likelihood' fitting method \citep{Gardner1980, Jones1980} by
implementing the function `arima' from the library `stats' of the R
programming language \citep{RCT2023}. The trends are reported together
with the \(2\sigma\) error. We observed a negligible change of
\(0.087\pm 0.08\,W/m^2/y\) on the mean OIR. Although, the previous
result is closer to the raw data, we preferred to present the annual
statistics, that give a more clear picture about the long term CE
trends. Hence, we calculated the annual values from the one-minute
measurements. Despite the very weak statistical significance of the mean
OIR trend, the annual number of CE occurrences shows a steady increase
of \(45.6\pm 21.9\,\text{cases}/y\)
(Figure\nobreakspace{}\ref{fig:P-energy-N}). Subsequently, the mean
annual energy of the CE events is increasing with a rate of
\(116.9\pm 67.8\,kJ/y\) (Figure~\ref{fig:P-energy-sum}), witch follows
the trend of the number of CE occurrences. We have to note that the
energy related to the CE events can not be directly linked with the
total energy balance of the atmosphere. The net solar radiation of the
region is not increased, but rather redistributed through the CE events.
This also is depicted by the ``instantaneous'' values of irradiance
(average over one minute), that can exceed the equivalent clear sky
irradiance to a considerable level.

@@

Another interesting aspect of the CE cases occurrences, is their
seasonal cycle. In
Figure\nobreakspace{}\ref{fig:relative-month-occurancies}, we have a
monthly box plot (whisker plot), where the values have been normalized
by the highest median value, that occurs on June. Although the number of
occurrences has a wide spread throughout the study period, the most
active period of CE occurrences is during May and June. During the
Winter (December -- February) the CE cases are about \(25\,\%\) of the
maximum. For the rest months the occurrences gradually ramp between the
maximum and minimum. These seasonality is a combinations of the clouds
occurrences, and the relevant position of the sun during the year.
Unfortunately, the lack of detailed data of cloud formation, type and
location is not allowing further analysis.

@@

The distribution of the CE over irradiance intensity follows an
exponential decline Figure\nobreakspace{}\ref{fig:ovir-distribution},
where there is an inverse relation between the events frequency and
events intensity. This is expected as, the stronger the CE events
become, the rarer the particular atmospheric and sun conditions will
occur. This is indicative to the magnitude and probability of the
expected OIRs events over Thessaloniki.

@@

\caption{Distribution of CE over irradiance magnitude.}\label{fig:ovir-distribution}
\end{figure}

@@

In order to further study the characteristics of the CE events, we
grouped the single minute CE events to continuous CE groups (CEG). Thus,
a CEG consists of one or more successive CE cases, and can represent
cloud enhancement conditions spanning a duration of multiple minutes. We
have identified 28468 groups, where the group with the longest duration
lasted 140 minutes on 07~July 2013. By examining the frequency
distribution of the CEG durations
(Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}), we can
conclude, that although we detected some CEG with durations longer than
an hour, about \(80\,\%\) of the CEG have a duration of less than 5
minutes.

@@

\caption{Distribution of CE groups duration in minutes.}\label{fig:ceg-duration-distribution}
\end{figure}
